The core transcriptome of mammalian placentas and the divergence of expression with placental shape

### 2017-03-08 manuscript/acronyms.tex
add OMA as an acronym
italicize C. elegans

@@

\DeclareAcronym{UNC93A}{short=\href{http://www.genenames.org/cgi-bin/gene_symbol_report?match=UNC93A}{\textit{UNC93A}},long={unc-93 homolog A (C. elegans)},first-style=reversed,single={\href{http://www.genenames.org/cgi-bin/gene_symbol_report?match=UNC93A}{\textit{UNC93A}} (unc-93 homolog A (C. elegans))}}
\DeclareAcronym{UNC93B1}{short=\href{http://www.genenames.org/cgi-bin/gene_symbol_report?match=UNC93B1}{\textit{UNC93B1}},long={unc-93 homolog B1 (C. elegans)},first-style=reversed,single={\href{http://www.genenames.org/cgi-bin/gene_symbol_report?match=UNC93B1}{\textit{UNC93B1}} (unc-93 homolog B1 (C. elegans))}}

>>>>

\DeclareAcronym{OMA}{short=OMA,long={Orthologous MAtrix project}}

@@

\DeclareAcronym{UNC93A}{short=\href{http://www.genenames.org/cgi-bin/gene_symbol_report?match=UNC93A}{\textit{UNC93A}},long={unc-93 homolog A (\textit{C. elegans})},first-style=reversed,single={\href{http://www.genenames.org/cgi-bin/gene_symbol_report?match=UNC93A}{\textit{UNC93A}} (unc-93 homolog A (\textit{C. elegans}))}}
\DeclareAcronym{UNC93B1}{short=\href{http://www.genenames.org/cgi-bin/gene_symbol_report?match=UNC93B1}{\textit{UNC93B1}},long={unc-93 homolog B1 (\textit{C. elegans})},first-style=reversed,single={\href{http://www.genenames.org/cgi-bin/gene_symbol_report?match=UNC93B1}{\textit{UNC93B1}} (unc-93 homolog B1 (\textit{C. elegans}))}}
